Reformulating phylogenetic mixed models to improve flexibility and speed

### 2019-07-08 phyloglmm_ms.tex
pushing to BB

%% CONT HERE, taking a break
\section*{Results}

@@

The simulations presented in this paper are an oversimplification of evolutionary processes in nature, but they are at least as complex as the models that researchers typically use.
Our results showed that even simple single predictor--response multi-species model could incorporate multiple levels of complexity.  
Fitting simpler variations can lead to unreliable estimates of the fixed effects, which are typically the quantities of interest.

@@

@@

We have presented the range of classical phylogenetic comparative methods (i.e. phylogenetic least squares, linear and mixed models) to fit models that incorporates different levels of phylogenetic variation.
Even within this scope, there is additional room for exploration we neglected, such as phylogenetic multivariate response models; non-Brownian evolutionary processes such as the Ornstein-Uhlenbeck (OU) model which accounts for both selection and drift processes \citep{butler2004phylogenetic}); Bayesian approaches \citep{hadfield2010general}; and variable-rate model, where evolutionary parameters vary across the phylogeny.
However, the simple approach we developed here offers an efficient way to handle phylogenetic comparative analysis for a wide range of univariate, Brownian-motion evolutionary models. 
This approach can in principle be combined flexibly with the state of the art phylogenetic mixed models using any platforms that supports independent latent variables such as Stan.
As always, users should be aware of the constraints of the amount of data they have relative to the complexity of the model they want to fit (i.e. What should we do when we don't have enough data? Should we use a complex model and overfit \citep{barr2013random}, the right balance of complexity and data \citep{baayen2008mixed}, singular fits or possibility of Bayesian approaches \citep{hadfield2010mcmc}).
More importantly, this implementation in \pkg{lme4} and \pkg{glmmTMB} allows users to fit phylogenetic mixed models to the fullest (large data, unbalanced species observations, complex random effects) and explore new ideas.

>>>>

\section*{Results}

@@

@@

The simulations presented in this paper are an oversimplification of evolutionary processes in nature, but they are at least as complex as the models that researchers typically use.
Even a simple single predictor--response multi-species model like the one presented above could incorporate multiple levels of complexity.
In theory, as long as there are a large amount of data and computational power to estimate model parameters (e.g., fixed and random effects), models that can incorporate a variety level of complexity always be better in capturing the system. 
However, it is rarely the case in real applications where ecologist and evolutionary biologist are constrained one way or another. 
As always, users should be aware of the constraints of the amount of data they have relative to the complexity of the model they want to fit (i.e., What should we do when we don't have enough data?)
and find the right balance of complexity and data \citep{baayen2008mixed}.
Being overly conservative by fitting simple models can lead to unreliable estimates of the fixed effects, which are typically the quantities of interest.
In contrast, being too ambitious can lead to overfitting where the data are unable to support. 
However, random-effect models (random-slopes models in particular) are almost always theoretically justified, but a given set of data may be insufficient to fit the correct model. 
In this case, overfitting the data with a maximal model may be better off than underfitting with a simpler model that have fewer data constraints \citep{barr2013random}.
Another possibility is to use Bayesian approaches with appropriate prior assumptions to aid convergence \citep{hadfield2010mcmc}.

@@

We have presented the range of classical phylogenetic comparative methods (i.e. phylogenetic least squares, linear and mixed models) to fit models that incorporates different levels of phylogenetic variation.
Even within this scope, there is additional room for exploration we neglected, such as phylogenetic multivariate response models; non-Brownian evolutionary processes such as the Ornstein-Uhlenbeck (OU) model which accounts for both selection and drift processes \citep{butler2004phylogenetic}); Bayesian approaches \citep{hadfield2010general}; and variable-rate model, where evolutionary parameters vary across the phylogeny.
However, the simple approach we developed here offers an efficient way to handle phylogenetic comparative analysis for a wide range of univariate, Brownian-motion evolutionary models. 
This approach can in principle be combined flexibly with the state of the art phylogenetic mixed models using any platforms that supports independent latent variables such as Stan.
More importantly, this implementation in \pkg{lme4} and \pkg{glmmTMB} allows users to fit phylogenetic mixed models to the fullest (large data, unbalanced species observations, complex random effects) and explore new ideas.
